Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-17 ebayes_rnaseq_heterosis.tex
start of experiment

% WML: Maybe it would be good to quickly clarify what a formal heterosis RNA-seq experiment is.

@@

>>>>

@@

An RNAseq experiment to identify genes demonstrating heterosis consists of three genetic varieties: two parental varieties (P1 and P2) and a cross between these two varieties called the hybrid (H). For each variety, replicate RNA samples are isolated and assessed for quality. cDNA libraries are constructed and the samples are sequenced. These libraries are sequenced

loaded on flow cells, and sequenced. The raw sequencing reads

\cite{nettleton2014design} and \cite{paschold2012complementation}
